---
title: "Outbreak of Febrile illness with cough and increased mortality -- Panzi Health Zone, DRC"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
#runtime: shiny
output:
  html_document:
    code_folding: hide
    code_download: true
    highlight: zenburn
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_collapse: no
    toc_depth: 3
    toc_float: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Introduction


```{r}

if (!require("pacman")) install.packages("pacman")

pacman::p_load(rio, 
               Hmisc,
               downloadthis,
               flextable,
               stringdist,
               tidyverse)

pacman::p_install_gh("deansayre/Rtesunate")
pacman::p_install_gh("const-ae/ggupset")
pacman::p_install_gh("moodymudskipper/powerjoin")


data_loc <- here::here("linelist", "LL_GPM_PANZI_23_01_2025_AS_RAJ.xlsx")

data <- rio::import(data_loc) %>% 
  Rtesunate::act_clean() %>% 
  rename(n = 1) %>% 
  mutate(id = row_number())

lab_loc <- here::here("linelist", "lab_linelist.xlsx")

lab_1 <- rio::import(lab_loc) %>% 
  Rtesunate::act_clean() %>% 
  select(-1) %>% 
  filter(!is.na(id)) %>% 
  filter(!is.na(noms))

lab_2 <- rio::import(here::here("linelist", "lab_linelist.xlsx"), which = 2) %>% 
  Rtesunate::act_clean() %>% 
  rename(id = labid) %>% 
  mutate(dte_de_reception = as.character(dte_de_reception)) %>% 
  filter(!is.na(id))


lab <- bind_rows(lab_1, lab_2) %>% 
  filter(!is.na(noms))

hf_dhis2 <- rio::import("dhis2_hf_names.xlsx") %>% 
  mutate(hf = case_when(str_detect(`kg Panzi Zone de Santé`, "Aire") ~ NA_character_, 
                                   .default = `kg Panzi Zone de Santé`),
         `kg Panzi Zone de Santé` = case_when(!is.na(hf) ~ NA_character_, 
                                              .default = `kg Panzi Zone de Santé`)
  ) %>% 
  fill(`kg Panzi Zone de Santé`, .direction = "down") %>% 
  filter(!is.na(hf))

hf_dhis2 %>% 
  Rtesunate::act_clean() %>% 
  rio::export(file = "hf_dhis2_usable.xlsx")


line_name <- word(data_loc, -1, sep = "/")  
line_last <- max(data$date_de_notification)

lab_name <- word(lab_loc, -1, sep = "/") 
lab_last <- max(lab$date_de_prelevement, na.rm = TRUE)
```

Line list data (file name _`r line_name`_) contains `r nrow(data)` observations, 
the most recent of which is dated `r line_last`.

Lab data (file name _`r lab_name`_) contains `r nrow(lab)` observations, 
the most recent of which is dated `r lab_last`.

## Data missingness
The number of missing observations for each variable are noted below. 
Note variables are listed in snakecase.
```{r}

b <- map(names(data), 
         function(.x){x = sym(.x)
         data %>% 
           filter(is.na({{x}}))
         }
)

missing_obs <- map(b, ~nrow(.x)) %>% 
  as_vector() %>% 
  as_tibble() %>% 
  add_column(Variable = names(data), 
             .before = 1) %>% 
  rename(`Observations Missing` = value) %>% 
  filter(variable != "id")


rm(b)

flextable::flextable(missing_obs) %>% 
  flextable::autofit()
  
```

## Spelling changes
Basic formatting and spelling changes are coded here. Explore code to review 
changes made, along with the Excel file below. 

```{r}


data_1a <- data %>% 
  mutate(tratement = str_replace_all(tratement, c("vit_c" = "vitc",
                                                  "vitce" = "vitc_vite",
                                                  "vit_ce" = "vitc_vite",
                                                  "vitace" = "vitc_vite",
                                                  "vita_c" = "vitc",
                                                  "vitac" = "vita_vitc", 
                                                  "vit_b12" = "vitb12",
                                                  "vit_b6" = "vitb6",
                                                  "at_60" = "at60", 
                                                  "para_injct" = "para-inject", 
                                                  "paracetamol_injct" = "para-inject",
                                                  "parainject" = "para-inject",
                                                  "para_inject" = "para-inject",
                                                  "para_inj" = "para-inject",
                                                  "acide_folique" = "acide-folique", 
                                                  "para" = "paracetamol", 
                                                  "artesunate_inj" = "artesunate-inj")
                                     )
  )# there will be an issue with entries containing multiple words as 
   # single entry when go to change pull individuals from these lists


data_char <- data_1a %>% 
  select(where(is.character)) %>% 
  select(-c(nom_et_postnom))

entered_values <- map(names(data_char), 
                      function(x){data_char %>% 
                          pull({{x}}) %>% 
                          unique()
                      }) %>% 
  set_names(names(data_char)) %>% 
  map(~as.data.frame(unlist(.x))
      )%>% 
  list_rbind(names_to = "variable") %>% 
  rename(entry = 2) %>% 
  arrange(variable, entry)

# uncomment below if need to update list of entries requiring spelling changes

#rio::export(entered_values, file = "entered_free_text.xlsx")

# spelling changes made and saved to separate file 'entered_free_text_with_spelling_change.xlsx'

spelling_changes <- rio::import("entered_free_text_with_spelling_change.xlsx") %>% 
  filter(!is.na(change_to))

data1 <- data_1a %>% 
  linelist::clean_variable_spelling(wordlists = spelling_changes,
                                    from = 2, 
                                    to = 3, 
                                    spelling_vars = 1)

data2 <- data1 %>%  
  mutate(age_unit = word(age, sep = "_", -1), 
         age1 = str_remove_all(age, paste0("_", age_unit)), 
         age2 = as.numeric(str_replace_all(age1, "_", "\\.")),
         age_years = case_when(age1 == "2ans" ~ 2, 
                               age1 == "4" ~ 4, 
                               age1 == "8_ans" ~ 8, 
                               age1 == "3mois" ~ 3/12,
                               age1 == "1omois" ~ 1/12, 
                               age1 == "18mois" ~ 18/12, 
                               age1 == "7mois" ~ 7/12, 
                               age1 == "1an" ~ 1,
                               age1 == "1ans" ~ 1,
                               age1 == "8ans" ~ 8,
                               age1 == "4_1_2" ~ 4.5, 
                               age1 == "3_ans_11" ~ 3+11/12,
                               age1 == "1_1_2" ~ 1.5,
                               age1 == "2_1_2" ~ 2.5,
                               age1 == "4_1_2" ~ 4.5,
                               age1 == "9mois" ~ 9/12,
                               age1 == "38a" ~ 38,
                               age_unit %in% c("m", "mois", "mos") ~ age2/12, 
                               age_unit %in% c("semaine", "semaines") ~ age2/52,
                               age_unit %in% c("ans", "asns", "an", "nas") ~ age2, 
                               .default = 999), 
         week = tsibble::yearweek(date_de_notification),
         paludisme_1 = case_when(paludisme == "palu" ~ "oui", 
                                 .default = paludisme), 
         tdr1 = case_when(tdr == "non.rensegne" ~ NA, 
                          .default = tdr)
         )

spell1 <- spelling_changes %>% 
 downloadthis::download_this(
    output_name = "panzi_spelling_change1",
    output_extension = ".xlsx",
    button_label = "Spelling Changes",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa-regular fa-arrow-down-to-line")

```

```{r echo=FALSE}

spell1

```



## Removal of duplicates


```{r}

rm(spell1)

####################################  search for duplicates using fuzzy matching
#### NOT complete as of 26 January, 2025. Response leadership to weigh in ######

# ensure Id provided is unique identifier
#  Hmisc::describe(data2$n)

data_dup <- data2 %>% 
  dplyr::select(date_de_notification, 
                name = nom_et_postnom,
                as, 
                sexe,
                age, 
                n) %>% 
  mutate(n = as.numeric(n)) %>% 
  full_join(., ., by = character()) %>% 
  filter(n.x < n.y) %>% 
  mutate(
    name.dist = stringdist(name.x, name.y), 
    as_same = as.x == as.y, 
    duration = lubridate::time_length(interval(date_de_notification.x, 
                                               date_de_notification.y), 
                                      "day")) %>% 
  filter(name.dist < 3) %>% 
  select(
    name.dist, 
    name.x, name.y, 
    sexe.x, sexe.y,
    date_de_notification.x, date_de_notification.y, 
    jours = duration, 
    as_same, as.x, as.y, 
    n.x, n.y) %>% 
  mutate(id_to_discard = NA) %>% 
  arrange(name.dist, jours, as_same)
  



# for manual examination
rio::export(data_dup, "doublants_possibles.xlsx")

doublants_vrai <- rio::import("doublants_possibles_vrai.xlsx")

data3 <- data2 %>% 
  filter(!n %in% doublants_vrai$id_to_discard)

dupes <- filter(doublants_vrai, !is.na(id_to_discard)) %>% 
 downloadthis::download_this(
    output_name = "panzi_dupes",
    output_extension = ".xlsx",
    button_label = "Duplicates",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa-regular fa-arrow-down-to-line")

```

A total of `r nrow(filter(doublants_vrai, !is.na(id_to_discard)))` duplicates
were removed, leaving a total of `r nrow(data3)` observations.


```{r echo=FALSE}

dupes

```

## Processing complication and treatment data
These data are entered as free text. Here they are standardized and processed
so as to be more useable.

```{r}


datatx <- data3 %>% 
  select(n, tratement) %>% 
  mutate(tx_list = str_split(tratement, "_")) %>% 
  filter(!is.na(tx_list)) %>% 
  unnest_longer(tx_list)

datatx_unique <- datatx %>% 
  select(tx_list) %>% 
  distinct(tx_list) %>% 
  arrange(tx_list)

rio::export(datatx_unique, "linelist/output/tratement_sp.xlsx")

treatment_spelling <- rio::import(here::here("linelist", 
                                             "output", 
                                             "tratement_sp_edit.xlsx")) %>% 
  filter(!is.na(change_to))

datatx_sp <- datatx %>% 
  left_join(treatment_spelling, by = "tx_list") %>% 
  mutate(tx_list_sp = case_when(!is.na(change_to)~ change_to, 
                                .default = tx_list)) %>% 
  select(n, tx_list = tx_list_sp) %>% 
  filter(tx_list != "rm") %>% 
  group_by(n) %>% 
  arrange(tx_list, .by_group = TRUE) %>% 
  ungroup() %>% 
  filter(!str_detect(tx_list, "^\\d")) 

treatment_list <- datatx_sp %>% 
  group_by(n) %>% 
  summarise(tx = list(tx_list)) %>%
  rowwise() %>% 
  mutate(tx1 = paste(unlist(tx), collapse = "_"))

unique(datatx_sp$tx_list)

data4 <- left_join(data3, treatment_list, by = "n") %>% 
  select(-tratement) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(any_artemisinins_a = list(map(c("act", 
                                          "artesunate",
                                          "aretesunate.rectal", 
                                          "asaq", 
                                          "artemether"),
                                        function(x) str_detect(tx1, fixed(x)))),
         any_artemisinins = any(any_artemisinins_a == TRUE), 
         any_abx_a = list(map(c("amoxicilline", 
                                "azithromycine", 
                                "ceftriaxone", 
                                "erytromycine",
                                "bactrim",
                                "genta"),
                              function(x) str_detect(tx1, fixed(x)))),
         any_abx = any(any_abx_a == TRUE), 
         complications = str_replace_all(complications, "broncho_pulmonaire", 
                                         "broncho.pulmonaire"))




data_comp <- data4 %>% 
  select(n, complications) %>% 
  mutate(list = str_split(complications, "_")) %>% 
  filter(!is.na(complications)) %>% 
  unnest_longer(list)


data_comp_unique <- data_comp %>% 
  select(list) %>% 
  distinct(list) %>% 
  arrange(list)

rio::export(data_comp_unique, "linelist/output/complications_sp.xlsx")

complications_spelling <- rio::import(here::here("linelist", 
                                             "output", 
                                             "complications_sp_edit.xlsx")) %>% 
  filter(!is.na(change_to))



data_comp_sp <- data_comp %>% 
  left_join(complications_spelling, by = "list") %>% 
  mutate(comp_list_sp = case_when(!is.na(change_to)~ change_to, 
                                .default = list)) %>% 
  select(n, list = comp_list_sp) %>% 
  filter(list != "rm") %>% 
  group_by(n) %>% 
  arrange(list, .by_group = TRUE) %>% 
  ungroup() %>% 
  filter(!str_detect(list, "^\\d")) 

comp_list <- data_comp_sp %>% 
  group_by(n) %>% 
  summarise(comp = list(list)) %>%
  rowwise() %>% 
  mutate(tx1 = paste(unlist(comp), collapse = "_"))

unique(data_comp_sp$list)

data5 <- left_join(data4, comp_list, by = "n")

################################################################################


############################################## clinical presentation ###########


# meets case definition? revision of case definition?


sympt_specific_out <- function(x, db){
  y <- sym(x)
  a <- db %>% 
    filter({{y}} == "oui") %>% 
    summarise(nombre = n(), 
              tpr = round(100*sum(tdr1 == "positif", na.rm = TRUE)/(sum(tdr1 == "negatif", 
                                                                        na.rm = TRUE) + 
                                                                      sum(tdr1 == "positif",
                                                                          na.rm = TRUE)),1),
              taux_mortalite = round(100*sum(evolution == "decede", na.rm = TRUE)/(sum(evolution != "decede", 
                                                                                       na.rm = TRUE)+sum(evolution == "decede", na.rm = TRUE)),2))
  
  return(a)
  }


a <- map(names(data3[14:30]), ~sympt_specific_out(.x, data3)) %>% 
  set_names(names(data3[14:30])) %>% 
  list_rbind(names_to = "presentation")

rio::export(a, "outcome_par_symptom.xlsx")

a_flex <- a %>% 
  mutate(presentation = str_to_title(str_replace_all(presentation, "_", " "))) %>% 
  arrange(-nombre) %>% 
  rename("Symptômes" = presentation, 
         "Nombre de Cas" = nombre, 
         "Taux de positivité - TDR (%)" = tpr, 
         "Taux de mortalité (%)" = taux_mortalite) %>% 
  flextable::flextable() %>% 
  flextable::colformat_num(big.mark = "", digits = 1) %>% 
  flextable::autofit()

flextable::save_as_docx(a, path = paste0(here::here("linelist", 
                                                    "output", 
                                                    "symptom_outcome_all.docx")))

outcome_by_presentation <- data3 %>% 
  select(n, 14:30) %>% 
  pivot_longer(-n) %>% 
  filter(value == "oui") %>% 
  group_by(n) %>% 
  mutate(list_sympt = list(name)) %>% 
  ungroup() %>% 
  left_join(select(data3, n, tdr1, evolution), 
            by = "n") %>% 
  group_by(list_sympt) %>% 
  summarise(count = n(), 
            tpr = round(100*sum(tdr1 == "positif", na.rm = TRUE)/(sum(tdr1 == "negatif", 
                                                                      na.rm = TRUE) + 
                                                                    sum(tdr1 == "positif",
                                                                        na.rm = TRUE)),1),
            taux_mortalite = round(100*sum(evolution == "decede", na.rm = TRUE)/(sum(evolution != "decede", 
                                                                                    na.rm = TRUE)+sum(evolution == "decede", na.rm = TRUE)),1)
  ) %>% 
  arrange(-count, -taux_mortalite, -tpr)


missing_one <- outcome_by_presentation %>% 
  rowwise() %>% 
  filter(!all(c("fievre", "toux") %in% list_sympt)) 
  
missing_both <- outcome_by_presentation %>% 
    rowwise() %>% 
    filter(!any(c("fievre", "toux") %in% list_sympt)) 
  
symptom_combos <- map(list(outcome_by_presentation, missing_one, missing_both),
    ~.x %>% rowwise()%>% 
      mutate(list_sympt =  str_to_title(paste(list_sympt, collapse = ", ")), 
             list_sympt = str_replace_all(list_sympt, "_", " ")) %>% 
      rename(presentation_clinique = list_sympt, 
             tdr_positivite_pourcent = tpr, 
             nombre = count) %>% 
      ungroup()
)
    
symptom_combos_flex <- symptom_combos %>% 
  map(~.x %>% 
        rename("Symptômes" = presentation_clinique, 
               "Nombre de Cas" = nombre, 
               "Taux de positivité - TDR (%)" = tdr_positivite_pourcent, 
               "Taux de mortalité (%)" = taux_mortalite) %>% 
        flextable::flextable() %>% 
        flextable::colformat_num(big.mark = "", digits = 1) %>% 
        flextable::autofit()
      )

map2(symptom_combos_flex, 
     list("symptom_outcome_all", "symptom_outcome_missing_fever_and_or_cough", 
          "symptom_outcome_missing_both_fever_and_cough"), 
     function(x, y){flextable::save_as_docx(x, path = paste0(here::here("linelist", 
                                                                        "output"), "/", y, ".docx"))
     })



################################################################################
#############################################  complications ###################




```

